% Created 2023-05-03 Wed 13:20
% Intended LaTeX compiler: xelatex
\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\setlength{\parskip}{1em}
\setlength{\parindent}{0em}
\frenchspacing
\usepackage{hyperref}
\hypersetup{colorlinks=true}
\hypersetup{urlcolor=blue}
\usepackage{fontspec}
\setmainfont{Charter Roman}
\setsansfont{IBM Plex Sans}
\setmonofont{iA Writer Mono S}
\author{Paul Menair}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Paul Menair},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 28.2 (Org mode 9.4.6)}, 
 pdflang={English}}
\begin{document}

\section*{Leibel Law}
\label{sec:orgfbf6d77}

\subsection*{Adams, Shawn v. Volle et al.}
\label{sec:orga5eeffe}

\emph{Shawn Adams v. Luke Volle and Carl Volle}

Counsel for Ds(Auto Owners): \href{https://gabar.reliaguide.com/lawyer/30309-GA-William-Casey-272796}{William T. Casey, Jr., Swift, Currie, McGhee \& Hiers, LLP}

Counsel for Ds(Auto Owners): \href{https://gabar.reliaguide.com/lawyer/30533-GA-Amber-OConnell-282120}{Amber R. O’Connell, Swift, Currie, McGhee \& Hiers, LLP}

Good imaging report on disc herniation suggesting acute C6-7 and L5-S1, possible hamstring tear; good liability case, significant damage, solid medical. RFAs admit family purpose. Driver admits partial fault, denies failing to yield. Depos done - NB encounter at auto body shop. Progressive out on Yarb. Discovery over, mediation failed. Son says his father needs help lifting, not visibly in pain. Medical should be up to date, FF identified. Demand withdrawn re surgery needed, future medicals.

NB Pl OOS 99,999.99

Dave Seecharan is doing the surgery, funding company is reviewing medical for approval of the operation. Lots of lien.

\begin{itemize}
\item \textit{<2023-05-03 Wed> } Todo: [Adams] PP for trial, need notice of intent to go out, etc. Looks like it might go 5/22 bc Sullen maybe ain't --> doctor depo?

SURGERY 4/24 pp for trial weeks of May 22 and July 12 [NB conflict with Sullen first week, Peterson 2d week]

client getting surgery, doctor depo, id as treating, per skl no MIL re shop, need notice of intent, voir dire, charges. Set up court reporter per order. getting employer as FF Cabot rejected case
\end{itemize}

\subsection*{Alevy, Laura v. Wheeler}
\label{sec:orgf31405d}

\emph{Laura Alevy v. Donald A. Wheeler}

Counsel for Defendant (LI): \href{https://gabar.reliaguide.com/lawyer/30091-GA-Christine-Proctor-272295}{Christine Proctor, Lynn Leonard \& Associates}

Counsel for UM: \href{https://gabar.reliaguide.com/lawyer/30043-GA-Abiemwense-Oyegun-278090}{Abi Ogeyun, Allstate}

TBI, depos done, D wants to apologize, admits liability. Gaps in treatment. Encompass UM add-on, dismissed on Yarb, atty no longer with firm. NB overseas providers.

Discovery ran 11/30. They identify Baugh as neuro expert in January (mild concussion only, gap in treatment); we now have a neuro showing TBI. [Daughter (Lana) is FF], UM is back in. They sent OOS. Client does not recall approving 50k offer, must have been prelit.

Trial - Depose Mahalavich when we're closer, get illustration of type of TBI. 

Identified Harben, McCord, and Eisenman. Get folks from her department to testify.

\begin{itemize}
\item \textit{<2023-05-12 Fri> } Follow up: [Alevy] settle and get into the slip and fall, just ff (woman from Lebanon), don't worry about treatment, did we suppl cognitive report?
\end{itemize}

\subsection*{Bromaghim, Stephanie v. Ligon et al.}
\label{sec:orgb83593d}

\emph{Stephanie Lynn Bromaghim v. Lee Ann Ligon and Dan Siler}

Counsel for Defendants: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=NjI2MTc2}{Jessica Sanford, Fain Major \& Brennan PC}

Counsel for UM: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=NzcwNjEw}{John W. Wingate III, Myers \& Wingate LLP}

Client still has issues and is actively treating with injections again, UM out. Need MIL re conduct at the scene, special set, Daubert. Discovery ran 2020-11. Stip to trial by D. We will use treating live as an expert.

\href{https://www.fastmail.com/mail/Action\_-\_Follow\_up/Mde43c64c6fa1836e114528ec?u=737c4181}{Get 1099s for Negrin}. NB they have a second expert now, Aloice Aluoch, a rheumatologist, cancelling depo

--> get record designation ready. 

OOS for 500k

OOS? update medical? No records found re phone.  PTO and Negrin cross, get list of cases and 1099s. Update chronology from India. They admit breach and causation of the accident but unable to admit or deny negligence

\begin{itemize}
\item \textit{<2023-05-12 Fri> } Follow up: [Bromaghim] FF BW setting up depos. Depose McDonald, rely on Alouch. DO NOT use comp file. SKL to talk to Marks, SC to look at Negrin report.
\end{itemize}

\subsection*{Bruce, Matthew v. Kroger Co.}
\label{sec:org77a5686}

\emph{Matthew Bruce v. The Kroger Co.}

Counsel for Defendant: \href{https://gabar.reliaguide.com/lawyer/30326-GA-Matthew-Moffett-254910}{Matthew G. Moffett, Gray, Rust, St. Amand, Moffett \& Brieske, LLP}

Counsel for Defendant: \href{https://gabar.reliaguide.com/lawyer/30326-GA-Jeffrey-Wasick-268609}{Jeffrey M Wasick, Gray, Rust, St. Amand, Moffett \& Brieske, LLP}

\begin{itemize}
\item \textit{<2023-05-04 Thu> } Follow up: [Bruce] get squared away re damages, demand --> try direct negotiation per JW [he is out Thu - Mon]

\item \textit{<2023-05-30 Tue> } Deadline: [Bruce] discovery dl per minute order --> 6/25 msj or pto

--> supplement re experts, non-party --> review file re final supplement \href{file:///Users/pmenair/Documents/WORK SYNC/projects/5-CaseFiles/Bruce.org}{notes} UPDATE CABOT, SKL TO TALK TO KANCHERLA, FF, Cabot update based on new records
\end{itemize}

\subsection*{Conard, Victoria v. Ingles et al.}
\label{sec:org16a9bff}

Attorney for Ingles: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=NjI4MzI4}{James W. Scarbrough, Mabry \& McClelland, LLP}

Attorney for Ingles: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=MjQzNzkw}{William S. Carson, Mabry \& McClelland, LLP}

Attorney for Primo: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=MTM0MjIy}{Danielle C. Le Jeune, Cozen O'Connor}

Ingles admits control, won't admit or deny invitee. Will supplement re witnesses and video. No concerning defenses in 01-03 answer. No concerning defenses in Primo's 01-06 answer except "CPUS is an improper party\ldots{}"

Monthly inspection log provided and one page of policy, no video, daily logs, incident reports etc etc

All Primo produced was an invoice.

Liens. Client had knee disloc and sprain. Surgery, lots of PT and Tx with inject. Still wearing a brace as of 2023-04-10, pain, working home care.

\begin{itemize}
\item \textit{<2023-05-03 Wed> } Todo: [Conard] CALL WITNESS r file, scheduling depos, getting FCE, identify FF (fiance), etc, SKL to talk to doctor, get a lien on the file, maybe get a clean floor expert, BW getting prior records?

\item \textit{<2023-07-06 Thu> } Deadline: [Conard] discovery dl per answers
\end{itemize}

\subsection*{Dawson Village}
\label{sec:org03fcc7d}

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Dawson Village] check bill, service status, filing new compl
\end{itemize}

Generally, when a landlord evicts a tenant and takes possession of the premises, the lease is terminated and the right to claim rent which accrues after eviction is extinguished. Bentley-Kessinger v. Jones, 186 Ga. App. 466, 467 ( 367 S.E.2d 317) (1988). However, the "parties to a lease agreement may contract in advance to hold the lessee liable for rent even after an eviction, deducting therefrom only the amounts recovered by the lessor from reletting the premises \ldots{} [if such an agreement is] premised on the existence of an explicit and detailed provision in the lease which clearly and unequivocally expressed the parties' intention to hold the lessee responsible for after-accrued rent even should an eviction take place." (Citation and punctuation omitted.) Id. at 467-468; Hardin v. Macon Mall, 169 Ga. App. 793 ( 315 S.E.2d 4) (1984).

Peterson v. P. C. Towers, L. P, 206 Ga. App. 591 (Ga. Ct. App. 1992)
Re future rent see Intl. Biochemical Indus., Inc. v. Jamestown, 262 Ga. App. 770 (Ga. Ct. App. 2003)

\subsection*{Day, Daniel v. McCartney et al}
\label{sec:org89f5b5a}

\emph{Daniel Ethridge Day v. Alan Lee McCartney and Linda Johanson} 

Counsel for Defendants(State Farm): \href{https://gabar.reliaguide.com/lawyer/30345-GA-Ann-Mandel-254226}{Ann Cox Mandel, Lynn Leonard \& Associates}

Counsel for UM(Progressive): \href{https://gabar.reliaguide.com/lawyer/30006-GA-Karolynn-Harris-252472}{Karolynn Harris, Worsham Corsi Scott \& Dobur}

Discovery is over. This is the case where we have the gas station video.

Discovery ran March 4, 2021, not going to depose anyone else re entrustment, primary liability is pretty clear. Medical mostly on lien, preexisting. Service defense withdrawn per discovery responses, which are good. Admit simple negligence. Client has continuing pain, we have video of the accident. Evaluation less than 2x bc gaps in treatment, lots of injections.

Medical needs work, doctor or expert, maybe life care plan or FCE. No OOS. No surgery bc no insurance, not a surgical candidate, SKL to talk to UM.

Let Johanson out? ACM found an additional 25k in coverage, also from State Farm

\begin{itemize}
\item \textit{<2023-05-04 Thu> } Follow up: [Day] talk to client re OOS, Cabot rejected case, update medical, get depo, waiting on decision re msj
\end{itemize}

\subsection*{Deane, Tiffany v. Savage}
\label{sec:orgbe6d29b}

\emph{Tiffany Leigh Deane v. Patsy Jo Savage} 

Counsel for Defendant(Auto-Owners): \href{https://gabar.reliaguide.com/lawyer/30338-GA-Wayne-Tartline-248299}{Wayne Tartline, Bovis Kyle Burch \& Medlin LLC}

Counsel for Defendant(Auto-Owners): \href{https://gabar.reliaguide.com/lawyer/30338-GA-Precious-Okonokhua-387461}{Precious Okonokhua, Bovis Kyle Burch \& Medline LLC} \{Constantine Daniels instead now, but I don't think he's filed his substitution\}

Counsel for UM: \href{https://gabar.reliaguide.com/lawyer/30339-GA-Ashley-Rice-268185}{Ashley Rice, Waldon Adelman Castilla Hiestand \& Prout} \{PAID\}

Counsel for UM: \href{https://gabar.reliaguide.com/lawyer/30604-GA-Ellen-Lundergan-325742}{Zhengchan "Ellen" Lu, Waldon Adelman Castilla Hiestand \& Prout} \{PAID\}

D admits that she "inadvertantly caused" the collision, pled comparative fault, won't commit re no non-party fault. Hiding the ball on surveillance? Remember we spoke with the officer. 

Need MIL re referral from our office, DL. They are going to hammer her on the gap in treatment, operating without a license. SOL defense withdrawn. UM responses to discovery not great, but they tendered and we took their money. We are not going to identify Cabot, he's consulting only.

SC thinks meds are a little sketchy but "arguable" - MIL re DUI --> use son as adverse inference, r file re status - Discovery ran 9/19.

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Deane] Getting PPD rating, medical narrative from Axion, get more FF (best friend or minister), talk to mom, SKL to talk to spine doc and set up depo dates later for August (Julyish)

\item \textit{<2023-08-03 Thu> } Follow up: [Deane] depose officer and maybe doctor? Meet with 20yo and 15yo. Amend FF? Judge is going to put it on the October trial calendar.
\end{itemize}

\subsection*{Denson, Betty v. Gerteisen}
\label{sec:org6bea69a}

\emph{Betty Denson v. Donald Gerteisen and Linda Gerteisen}

Counsel for Defendants: \href{https://gabar.reliaguide.com/lawyer/30309-GA-Paul-Fields-256388}{Paul Fields, Fields Howell LLP}

Counsel for Defendants: \href{https://gabar.reliaguide.com/lawyer/30326-GA-Christopher-Lee-281365}{Christopher Sue-Min Lee, Fields Howell LLP}

AL co-counsel: \href{https://stokesstemle.com/attorneys/jonathan-h-stokes/}{Jonathan Stokes, Stokes Stemle, LLC}  <JStokes@StokesStemle.com>

Initially associate was Kathryn Shealy by notice of appearance, since withdraw per substitution of Christopher Sue-Min Lee. Supplement identifies Bruce Kofke (the realtor) as additional to the person at Vacasa, the builder, and the inspectors. The builder has nothing. PJI was sent 2019-12-31.

Tom Wright is rebuttal only. I discussed with SKL the consortium issue and we decided to wait; Court would probably not grant leave under the good cause standard. See rss discussion in notes.

Per Rhyder untreated aneurysm, could have caused fall. Headache? Pattern of blood classic for aneurysm, distinct, in addition to the trauma, if she had to guess that's what happened here. Post settlement discovery conference was 12/9. Response to msj filed 12/13.

EDF ID 11Cir is 430669620

\url{https://ecf.ca11.uscourts.gov/n/AttorneyFiling/login.jsf}
LeibelLaw
Oberdorfer7\#

\begin{itemize}
\item \textit{<2023-07-03 Mon> } Todo: [Denson] pp SKL for oral

\item \textit{<2023-07-17 Mon> } Event: [Denson] oral argument calendared, remember to look at rule re check in etc
\end{itemize}

\subsection*{Estes, Barbara v. Jim Hardman Buick GMC, Inc.}
\label{sec:orgdba070e}

\emph{Barbara Estes v. Jim Hardman Buick GMC, Inc. and Atlantic Leasing, LLC}

Counsel for Defendants: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=NjI4ODQw}{Stephen M. Schatz, Swift Currie McGhee \& Hiers LLP}

Counsel for Defendants: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=NTc1NzU3}{Lauren E.H. Meadows, Swift Currie McGhee \& Hiers LLP}

SOL 2021-12-17 trip and fall at a dealership. Answer for all Ds filed 2021-08-13, alleges JHA, Inc not a proper D, no other concerning defenses. Client hit her head, LOC, neck surgery recommended and done. Medpay 5k exhausted. Liens. Atlantic leased premises but did not have custody or control, JHB "operated a business" on the premises, denies custody or control. Jim Hardman, James Robert Anderson, Jim Hardman Buick GMC, Inc. 30b6, Michele Foitle/Tom Rumble; Rumble took the photos. ID'd Satterfield, never scheduled his depo, liability depos are done. Discovery ran 9/1.

continued, no PTO yet, take Grunch depo for preservation, supplement FF (called both on Fri)

TALK TO CLIENT RE ENT visit, prior thyroid - now has ear pain, headaches, new CT as of 12/1, lower back also but unrelated

\begin{itemize}
\item new adjuster, we sent demand for 650,000, wants to see if there is interest in continuing settlement discussion, she has authority for 75,000, trying to make a strong move, willing to talk about more

\item \textit{<2023-06-02 Fri> } Follow up: [EstesB] pp mediation? [I told the court June 12th, they are holding off, maybe update]

\item \textit{<2023-06-16 Fri> } Event: [EstesB] Mediation
\end{itemize}

\subsection*{Fugich}
\label{sec:org0968c31}

answer filed 2023-05-01

\begin{itemize}
\item \textit{<2023-06-05 Mon> } Follow up: [Fugich] look for discovery responses
\end{itemize}

\subsection*{Gade, Krishna et al. v. Wynn}
\label{sec:org54b57ce}

\emph{Krishna Gade and Mekala Srilatha v. Wynn Bevely}

Counsel for Defendant(State Farm): \href{https://gabar.reliaguide.com/lawyer/30060-GA-William-Anderson-283202}{Curtis Anderson, Downey \& Cleveland LLP}

Counsel for Defendant(State Farm): \href{https://gabar.reliaguide.com/lawyer/30343-GA-James-Cannella-267443}{James Cannella, Downey \& Cleveland LLP}

Counsel for UM (GEICO): \href{https://gabar.reliaguide.com/lawyer/30305-GA-Dennis-Manganiello-258810}{Dennis Manganiello, GEICO}

Cannella is denying basically everything in our RFAs. D admits liability in deposition, do we have his name right? Per skl miscarriage not legit. Discovery is run. Surgical estimate of 148,524.50 for Krishna. Mediation 9/14 failed, D has expert.

\begin{itemize}
\item \textit{<2023-05-26 Fri> } Follow up: [Gade] letter sent 4/13 WITHDRAW?
\end{itemize}

\subsection*{Hopkins v. Nelson et al}
\label{sec:org4967c30}

\emph{Christopher Todd Hopkins v. John Michael Nelson, Baldwin Paving Company, Inc., and Vertical Earth, Inc.}

Counsel for D: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=Nzk3OTUy}{Calvin P. Yaeger. Swift Currie}

Counsel for D: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=OTM0MjEw}{R. Alejandro Guarin, Swift Currie}

Counsel for Vertical: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=NDk1NTEz}{John L. McKinley, Jr., Mozley, Finlayson \& Loggins, LLP}

Counsel for Vertical: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=NzAzOTkx}{Jennifer T. McLean, Mozley, Finlayson \& Loggins, LLP}

genetic syndrome

contruction zone Forsyth accident SOL 2024-01-30, SEOS vertical earth filed 10-13, Nelson filed 10-18. Nelson and Baldwin answered 12/9 with no concerning defenses, no admission of vicarious liability per spurious "legal conclusion" assertion. Vertical Earth served 10/7, no answer. Went for an MRI, asked for neuroquant, Maloon talks about post-concussive. No presuit demands in file. Medpay 1,000 exhausted. NB we have plenty of body cam. No disposition on file. McCord hired, pending. Burns report?

Baldwin admits scope of employment, ownership of vehicle, denies direct negligence. Their driver denies liability, claims Hopkins was speeding and changed lanes suddenly, striking him. Safety manuals produced, no drug testing. Lots of objections, not clear if they are producing logs.

Sears, Roebuck Co. v. Ramey, 170 Ga. App. 873 (Ga. Ct. App. 1984) (insurance case)

Concussion case, treating with Maloon on lien, only neuro sypmtom per Maloon is headache, dizziness. Getting an expert (Eisenman?)

VE disco no witnesses, they got a reservation of rights letter prob bc of the indemnification issue, refuse to provide other legal action information, surveillance, safety director is Frank Dievbieere, Elliott Batts responded to rogs, no industry pubs. policy overly broad. no insurance claim docs, privilege per documents created, lots of issues but not clear how much they are a target.

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Hopkins] [hold informal discovery conf re docs?], scheduling depos D and Roeder, notice if no response by end of week.
\end{itemize}

--> Medical needs to be buttoned up. SKL to talk to clients about value, experts pending; update medical, demand? need before and after for expert

\begin{itemize}
\item \textit{<2023-05-11 Thu> } Event: [Hopkins] deposition of Bruce Roeder, ask about prior litigation etc

\item \textit{<2023-09-18 Mon> } Deadline: [Hopkins] discovery dl per VE Answer
\end{itemize}

\subsection*{Ivie v Senor Fiesta}
\label{sec:org9c75015}

\emph{Shelia Ivie v. Senor Fiesta \#2 LLC, Senor Fiesta \#3 LLC, and Rainer Hendon Dawson Marketplace Acquisitions I, LLC, State Court of Gwinnett County, 22-C-05919-S4}

Attorney for Ds: \href{https://gabar.reliaguide.com/lawyer/30319-GA-Michelle-Rossi-278195}{Michelle E. Rossi, Law Offices of Assunta S. Fiorini}

RHDMA Answer was due 11-21, extension filed discovery only 12/6, substitution filed 12/16 putting Rossi in as their counsel, no answer ever filed. Other Ds answered 12/2.

Answers filed with usual defenses 12/2, prior traversal, they want Senor 2 out but admit business invitee status as to Senor 3. Client has permanent partial disability. Lease produced. They are going to point to ETOH.

Case has liens, loss of use from elbow injury, inoperable.

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Ivie] rescheduling depos, client medical status, document production complete? Arellano no longer works there - EXTEND

\item \textit{<2023-06-02 Fri> } Deadline: [Ivie] discovery dl per answers

\item \textit{<2023-07-25 Tue> } Event: [Ivie] client depos
\end{itemize}

\subsection*{Keller, Olivia v. Olivia Wilson et al.}
\label{sec:org6eabd50}

\emph{Olivia Keller v. Olivia Wilson and Jason Wilson}

Counsel for Defendants: \href{https://gabar.org/MemberSearchDetail.cfm?ID=NTg2NDU2}{James Wysocki, Law Offices of Assunta Fiorini (Farmers)}

Migraines (neck trauma?), lower back pain radiates, leg weakness, epidurals, nerve block, dry needling, meds (Lyrica, Tramadol), kids in the car. Talking about device, surgery. We sent her to a different neuro. Both were insured through work. UM out on Yarb.

3MM UMBRELLA ON LI SIDE

Per SKL client TBI headaches, hearing, memory, obgyn, big brain. sent to Weber (Neuro) and Combier for review. Medicaid.

Birthday, winery, not drinking, just turned in front, clear liability. No conversations with my client. Disinterested witness with dashcam, willing to talk. Might have. His client has video going around car.

Olivia 414877580 SSN
770-314-7823 ATT Jason Wilson
Father 4045975286

No service defense per Wysocki, DOL 2020-11-24

Per Wysocki, this is really a damages case, regardless of what Olivia says. Liability not an issue.

Discovery ran 3/6 --> D depos done, set up Zoom with other P, fu Pl depo, get medical in order

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Keller] RESERVE UM? (NO), update meds, add claim for future surgery, getting narrative with estimate --> mediation? Demand limits on 250k? Maybe SKL talk to Wysocki
\end{itemize}

\subsection*{Kohler, Robert v. Carroll}
\label{sec:org708775f}

\emph{Robert Kohler v. Karen Carroll}

Counsel for D: \href{https://gabar.reliaguide.com/lawyer/30603-GA-William-Cowsert-257518}{William Cowsert, Cowsert Heath LLP}

Counsel for D: \href{https://gabar.reliaguide.com/lawyer/30603-GA-Susan-Elder-248758}{Susan Elder, Cowsert Heath LLP}

Counsel for UM: \href{http://martensonlaw.com/attorneys/e-alan-miller/}{Alan Miller, Martenson Hasbrouck \& Simon LLP}

Counsel for UM \href{https://gabar.reliaguide.com/lawyer/30326-GA-William-Prosch-309435}{Trey Prosch, Martenson Hasbrouck \& Simon LLP}

D Answer filed 2021-06-09, no concerning defences, admits negligence and causation of the collision. RFAs point to the fact that this was a chain reaction accident.

Trey Prosch / Al Miller UM Southern/Donegal Insurance, carrier for employer. He says personal UIM has 500k? 404-909-8116. Neck surgery, recovering from back surgery.

D admits liability, discovery responses clean. She's hiding behind the chain reaction. But the issue is dealt with by stipulation now, with the other parties dismissed.

No concerning defenses in UM answer. Supplementing FCE. Amber (former spouse) 706-968-6364, father 770-654-9605, they may have contacted.

January discovery responses re discovery from McBrayer to Carroll trying to set up an attorney fee claim

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Kohler] STIP TO TRIAL CALENDAR SKL to talk to Belknap then take deposition, looking into pain mgt

get officer affidavit? no motion filed yet

No property claim, they paid (too little, but we got the check)
\end{itemize}

\subsection*{Kridel, Geoffrey v. MCD}
\label{sec:org3eaed2b}

Counsel for all Ds: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=ODg5MDky}{John Alexander Hannay, American Family}

Slip and fall at McDonald's, all entities answered with no concerning defenses as of 7/22

discovery ran 4/24

\begin{itemize}
\item \textit{<2023-05-04 Thu> } Follow up: [Kridel] fu ocn re torres [document let us know if you knew where to find him? mail subpoena? get dates] RFA nobody recalls fall

do not contact employees - doctor depo waits for after msj
\end{itemize}

\subsection*{McKinney v. Jenkins \& Stiles et al.}
\label{sec:orged37448}

Forklift accident in TN - NB answer points finger at other parties, being handled by TN counsel

fu re firearms

\subsection*{McMullen, Shirley [Davis, Patricia] v. Jones}
\label{sec:orgdd25578}

\emph{Patricia Mercner Davis, individually, as wrongful death claimant, and as personal representative of the Estate of Shirley Mercner McMullen, deceased, and Lynn Hyde and Randy Mercner v. Keira Jones, Jean Jespersen and Michael Jespersen}

Counsel for Defendant: \href{https://gabar.reliaguide.com/lawyer/30319-GA-Michael-Moore-273655}{Michael J. Moore, Strickland \& Schwartz, LLC}

Counsel for Counterclaim Defendant: \href{https://gabar.reliaguide.com/lawyer/30006-GA-Cynthia-Bower-270882}{Cynthia Bower, Worsham, Corsi, Dobur \& Berss}

SOL 2023/02/08, this is a death case, they want to tender 100k, we want to go after the individual D, who is 17. Family purpose part is important for this one, we are going for property not coverage. Waiting on accident report, estate. Speeding citation three days prior. We got the UM 100k. Where is she at school, get transcripts

404-915-6156 Cynthia Bower - Melvina for scheduling

They are alleging our client went through a yellow signal. Witness in building near intersection. Jennifer Norris, 7702892808, saw green signal in lane D was turning into immediately after crash, did not see the crash. They sent us a copy of 40-6-73, but we properly alleged violation of 40-6-71? Only witnesses identified in rogs are those in the accident report. NB criminal case ongoing. Counterclaim dismissed without prejudice. Are insurance coverage issues sorted? Family purpose established as to mom. Get our own reconstruction person? OOS?

--> hold re experts, discovery ran 2023-05-01

\begin{itemize}
\item \textit{<2023-05-15 Mon> } Follow up: [McMullen] meet with client to get authority to take consent judgment after msj briefing filed.
\end{itemize}

\subsection*{Moye, Sheria v. Black et al.}
\label{sec:org04c4a14}

\emph{Sheria Moye v. Emily Anne Black, MD, Kimberly Stanley, Jacob Dickson, Northeast Georgia Medical Center, Inc., Northeast Georgia Physician's Group, Inc., Monitoring Concepts Neuro, LLC, and US IOM, LLC}

Counsel for Black, NGPG, NEGMC: \href{https://gabar.reliaguide.com/lawyer/30309-GA-Michael-Bailey-248155}{M. Scott Bailey, Huff, Powell \& Bailey, LLC}

Counsel for Black, NGPG, NEGMC: \href{https://gabar.reliaguide.com/lawyer/30309-GA-Lindsey-Costakos-279062}{Lindsey L. Costakos, Huff, Powell \& Bailey, LLC}

Counsel for Stanley, Dickson and monitoring entities: \href{https://gabar.reliaguide.com/lawyer/30303-GA-Terrell-Benton-263119}{Terrell W. Benton, III, Hall Booth Smith, PC}

Counsel for Stanley, Dickson and monitoring entities: \href{https://gabar.reliaguide.com/lawyer/30303-GA-Sheila-Kazemian-281971}{Sheila K. Kazemian, Hall Booth Smith, PC}

Service complete as of 12/17; NB jxn denials in RFA responses.

Answers: No concerning defenses as to most defendants except to venue. Dickson out.

See notes. NB battery and informed consent malpractice are DIFFERENT THINGS, general consent is a defense to battery claim

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Moye] supplement new expert, FF, discovery extend filed WAIT FOR THEM TO SCHEDULE EXPERTS, amend to add punitives against doctor, maybe fraud? - fu re the screenshots, broader scope of audit trail, FF, fu ltr re msgs

\item \textit{<2023-06-23 Fri> } Deadline: [Moye] discovery dl per extension
\end{itemize}

\subsection*{Nater, Paul v. Redfern}
\label{sec:orga05371e}

Counsel for Defendant: \href{https://gabar.reliaguide.com/lawyer/30345-GA-Alaina-Howard-107788}{Alaina S. Howard, Lynn Leonard \& Associates}

Counsel for UM: \href{https://gabar.reliaguide.com/lawyer/30060-GA-Ryan-Ingram-272652}{Ryan Ingram, Moore Ingram Johnson \& Steele LLP}

Counsel for UM: \href{https://gabar.reliaguide.com/lawyer/-GA-Yasmin-Cunningham-175027}{Yasmin R. Cunningham, Moore Ingram Johnson \& Steele LLP}

DOL 2019-10-23 They identify State Farm personnel in discovery? No responses re prior litigation, limited medical detail provided except that he was on an antibiotic. Client lives in FL. We produced financial info for Karen, her loss of income because she had to move with her husband is part of the claims, need to put numbers on all of this though. D pled nolo, is crazy and armed. Significant collision. D looks much more injured than client at scene. He claims sudden medical emergency, client told officer he had to stop suddenly.

Acute headache at hospital day of collision, MRI normal, back pain "feels like it's muscular," no Fx, no radiculopathy. Tinnitus maybe due to Rx (my guess)? Chronic neck and shoulder pain after, did PT, RFA, injxn. 2d MVA in 2021. They contend not related. Cabot on review suggests headaches have resolved, he can't speak to the tinnitus, thinks that the sprain exacerbated pre-existing facet arthritis, possible causation of shoulder tear but he is unclear. We sent an OOS for \$150,000. 

Bad neuro, do not produce. ADDED CONSORTIUM, discovery ran 6/2

\begin{itemize}
\item DO NOT amend for punitives, client needs to get to new expert, maybe do policy limit OOS (clear with client). Need settlement statement, figure out liens. cell phone?

Lots of lien

\begin{itemize}
\item figure out why they are not using the new caption - review re status, discovery is over, authorize and send?
\end{itemize}
\end{itemize}

SENDING TO NURSE ASHLEY

\subsection*{Nelson, Curtis}
\label{sec:orgd34c01a}

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Nelson] service BONINE NON EST- SOL 11/23/24 - wait for answers and find him
\end{itemize}

Get photographs

Tire tiering press

when tire is curing, different areas in mold pulls air out, when clogs happen there are issues, when into the press, fix anomalies, that was his duty that day

spring vents, little rubber hairs vent out of mold, rubber closes valve, inside of the mold, valve gets stuck down, vibrate ultrasonically

training in mold shop, start on cold molds

"mold shop bike guy"

500 curing presses

also cleaning and assembling and installing molds

bladder inside tire while it molds

bladder valve faulty, heated nitrogen, let in pressure, blew off clamp, came up around legs and burned them

molds designed by Toyo, container is made by another company, curing press itself made by another company - kitsuno?

Advance Technology for maintenance, changed in January went in house

Faulty check valve beneath curing press

Told past issues, assume work orders, not fixed

---

safety Bonine, formerly ATS, now curing supervisor

redness and scarring, inflammation, static feelings and pain

\subsection*{Peace}
\label{sec:org5e98caa}

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Peace] file, service compl dol 2021-10-15, discovery responses to UM due 5/25, give away to Hollingsworth
\end{itemize}

\subsection*{Peterson, Ginger v. Walmart}
\label{sec:org44aef7c}

\emph{Ginger Peterson v. Walmart, Inc, Wal-Mart Real Estate Business Trust, and Wal-Mart Stores East, LP}

Counsel for WalMart: \href{https://gabar.reliaguide.com/lawyer/31708-GA-Mark-Pickett-246349}{Mark Pickett, McLain \& Merritt PC}

Counsel for WalMart: \href{https://gabar.reliaguide.com/lawyer/30326-GA-Ernest-Beaton-253895}{Ernest L. Beaton IV, McLain \& Merritt PC}

Walmart denies liability, video slip. We have the shoes. Total hip. Client saw nothing on floor. Client and husband worked for Walmart. Service defenses as to the real estate trust but they admit WMS East controls the premises. We interviewed the Subway guy, he thinks it was the shoes, do not depose.

Not a great case on liability. Discovery ran 11/23, MSJ pending, not sure if we ever had a post-discovery settlement conf.

[ ] Exchange demostratives
[ ] supplement exhibit list
[ ] witness 30b6 name her
[ ] demonstratives - recovery time etc DAMAGES
[ ] look for camera 13

\begin{itemize}
\item \textit{<2023-05-03 Wed> } Todo: [Peterson] JURY CHARGES trial prep / conflict letter / calendar dls

\item \textit{<2023-06-05 Mon> } Event: [Peterson] pretrial conf

\item \textit{<2023-06-12 Mon> } Event: [Peterson] trial
\end{itemize}

\subsection*{Ragsdale, Forest}
\label{sec:org1870cae}

\emph{Forrest Ragsdale v. Wells Fargo Bank National Association (Inc.), CBRE, Inc., 5405 JCB Holdings, LLC, and John Does 1-10}

Counsel for Wells Fargo and JCB Holdings: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=NDA5NTA5}{Dawn Pettigrew, HUDSON LAMBERT PARROTT WALKER, LLC}

Counsel for Wells Fargo and JCB Holdings: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=NTk1OTk5}{Brad Parrott, HUDSON LAMBERT PARROTT WALKER, LLC}

Counsel for CBRE: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=NTI4Mjgx}{Elliot C. Ream, Hawkins, Parnell \& Young, LLP} x7424

Wells Fargo answered 2022-10-12 with no concerning defenses. CBRE answered per opened default 1/23, no concerning defenses

LOTS OF PREEXISTING, neuro, psych, incontinence, lower back pain.

\begin{itemize}
\item \textit{<2023-05-03 Wed> } Todo: [Ragsdale] pp topics for 30b6 of CBRE, Bank, Azar, email counsel re dates, r file

Eliott getting information re Azar, or do non-party/30b, review notes re next steps, depos --> schedule depos, when did they fix it? FIND OUT ABOUT INSPECTION, CURRENT, finalize id experts [see notes]

\item limit somehow
\item "The parties agree that the Employee did not suffer a catastrophic injury (solely as defined under OCGA § 34-9-200.1(g)."

\item \textit{<2023-07-24 Mon> } Deadline: close of discovery per CBRE answer
\end{itemize}

\subsection*{Reeves, Lord v. Skiles et al}
\label{sec:orged51e88}

\emph{Lord W. Reeves and Brittany Day v. Trevor Skiles, Concrete Pump Partners, LLC, and Westfield Insurance Company}

Counsel for all Defendants: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=MDc5NzU0}{Thomas E. Brennan, Fain Major \& Brennan PC}

Counsel for all Defendants: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=MTQxOTMx}{Robert Hoyland, Fain Major \& Brennan PC}

DOL 2020-08-26, 150k+ damages, good accident per vehicle photos, they will stip to liability.

Westfield responded to RFAs, admits process but denies SMJ (probably allege direct action does not apply). discovery sent 8/12, responses late

Per Wellstar no LOC but hit head, complains back and leg pain post roll over MVC, Hx lumbar fusion, no acute Fx in CT, "no obvious traumatic injuries," ordered fu incidental cardiology findings.

Maloon treat for concussion, vestibular dysfunction and mild hearing impairment, migranes, cognition. MRI shows white matter changes but consistent with age, no significant abnormality. Later records note he is treating ortho for neck and shoulder pain, but initial visit reported pain in lumbar spine. Anxiety etc.

Per Maloon He's pretty level, at status quo or "MMI if you like," but still with lots of deficits, no further testing required. Need to move on, no more management, cognitive impairment and headaches and vestibular.

AOI did injection and then total arthroplasty C5-6 Op note shows osteophytes compressing cord, consistent with our claim per SKL

\begin{itemize}
\item \textit{<2023-05-03 Wed> } Todo: [Reeves] \{see below\} --> fu with SC re expert designations --> next step

--> deal with remaining 6.4, depos, schedule SC is working on identification, name hinrich [he is going to look at new neuro first], get names of their experts, who are they going to name, per Brennan they are waiting on non-parties before discovery depos. I had worked out a lot of the 6.4 with Hoyland but not sure I documented? He was going to supplement\ldots{}

[ ] safety guy as 30b6 policies and procedures, training, hiring, supervision
no formal training for driving a cement truck. [PDM]

[ ] find a training expert [PDM] - call Reeves if he knows a training guy

[ ] scheduling our treating experts [BW] Malcolm and Maloon for now, ask Doc if they will agree to Zoom testimony

\item \textit{<2023-10-02 Mon> } Deadline: [Reeves] discovery dl, pto or msj due by 11/3
\end{itemize}

\subsection*{[Riley] Carey, Melissa indiv. and as PR et al. v. GNI et al.}
\label{sec:orgf5423dc}

\emph{Melissa Riley Carey, individually and as Personal Representative of the Estate of Matthew Wallace Riley, and Wallace Riley v. Georgia Neurological Institute and Dr.Hugh F. Smissson III}

\emph{Melissa Riley Carey, individually and as Personal Representative of the Estate of Matthew Wallace Riley, and Christina Greenberg Riley, as Personal Representative of the Estate of Wallace Riley v. Georgia Department of Corrections et al.}

Counsel for doctors: \href{https://gabar.reliaguide.com/lawyer/30309-GA-Michael-Bailey-248155}{M. Scott Bailey, Huff, Powell \& Bailey, LLC}

Counsel for doctors: \href{https://gabar.reliaguide.com/lawyer/30309-GA-Jeffrey-Braintwain-265975}{Jeffrey D. Braintwain, Huff, Powell \& Bailey, LLC}

Counsel for DOC: \href{https://gabar.reliaguide.com/lawyer/30334-GA-Peter-Fisher-276932}{Peter Fisher, Georgia Office of the Attorney General}

Counsel for 1983 Ds: William Winford Peters, Georgia Office of the Attorney General -- Not in bar directory, wpeters@law.ga.gov

Caylor v. Potts, 183 Ga. App. 133 (Ga. Ct. App. 1987) wrongful death action survives to his estate

Client is in Chap 13, but no indiv. capacity claims in either action. We were going to get certified CMB but not sure we need it any more?

Fisher cell 623-606-7932

David P. Folkenflik
5742 54th Ave N
St Petersburg FL
7275484529

Post-discovery conference conducted on 05/23

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Riley] stip to trial? look into preacher, maybe get economist, expert re utilization management
\end{itemize}

\subsection*{Scantland, David v. French}
\label{sec:orgc9e05f3}

\emph{David Scantland v. Kelci French}

ppeele@meyn.com

Counsel for Defendant: R. Russell Grant, Cruser, Mitchell, Novitz, Sanchex, Gaston, \& Zimet, LLP - no longer with firm, no substitution?

Counsel for Defendant: \href{https://gabar.reliaguide.com/lawyer/30092-GA-Timothy-Mitchell-276517}{Timothy L. Mitchell, Cruser, Mitchell, Novitz, Sanchez, Gaston, \& Zimet, LLP} Cell: 810-348-1942

Counsel for Progressive: \href{https://gabar.reliaguide.com/lawyer/30308-GA-Terry-Strawser-256088}{Terry L. Strawser, Worsham Corsi, Dobur \& Beress}

Joe Kania joseph\textsubscript{p}\textsubscript{kania}@progressive.com 908-601-7486

SOL 3/24. USAA has 100k LI, Progressive has 25k add on UM. Preexisting cervical, see 2015-07-16 MRI disc protrusion, but record confirms posttraumatic protrusion. Headaches and blurry vision post-MVA. Post-accident fall caused by sciatic pain. \$21,894.20 medical as of 7/19, needs update. Per CS value at 35-40k. HOWEVER, surgical recommendation; he got bariatric surgery to lose weight for the back procedure. We made policy limits demand to USAA, their top offer was \$32,225, litigation OOS 100,000. 

Progressive answer 4/9 with no concerning defenses. French is in default. Will need to update medical. Other driver filed in 2019. Rear end, client was middle car, stopped for vehicle turning left. Vehicle total loss. Per default order discovery is damages only.

Response to UM discovery sent -- service was notorious -- serve UM discovery? Fitts fishing re Yarb. I reviewed his discovery responses, which were pretentious and annoying and generally withholding, but suggest no 6.4. They will stip to coverage.

Rogs and RFD, they produced what looks like the whole claim file, lots of objection to e.g. medical rogs on the ground that they stipulated liability. Many references to the other case.

No OOS per SKL, work on the medicine. Floyd recorded statement produced. Per SC spine is related, not ocular, not good for tbi bc ETOH, psych, and lack of other evidence. Most recent neuro relates to spine per doctor.

Wallis v. Cotton States Mut. Ins. Co., 182 Ga. App. 147
Cherokee Ins. Co. v. Lewis, 204 Ga. App. 152

Re UM, interesting problem for Stephen

Discovery ran 9/30/22. 

---

KEEP TRACK OF TIME

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Scantland] agendaskl re Casey email (headaches are cervical not TBI, cognitive is vascular disease) [we have a liability determination] / update medical / SKL to depose doctor, FF, loss work flesh out, capacity, urology
\end{itemize}

\subsection*{Schuch, Daniel v. MasTec}
\label{sec:orgb1c3792}

\emph{Daniel Schuch and Angelique Schuch v. Ace American Insurance Company, MasTec North America, Inc., MasTec, Inc., and Douglas Whitt}

Counsel for Ds: \href{https://www.cozen.com/people/bios/tidwell-thomas}{Tom Tidwell, Cozen O'Connor}

Counsel for Ds: \href{https://gabar.reliaguide.com/lawyer/30309-GA-Danielle-LeJeune-277942}{Danielle Le Jeune, Cozen O'Connor}

SOL 2021-06-25; removed and then remanded. Witness interview on file. FCE shows lumbar impairment, TBI. Guilty disposition on failure to obey signal, t-bone accident. Liens. Lots of docs produced including telemetry. Denial of liability, admit scope of employment. Witnesses: Defendant Douglas Whitt, Roger Hopper, Butch Christian, Meredith Goss, Forsyth County Sheriff’s Office Deputy Zachary Archer. He was delivering repair parts, no bill of lading. 

CONFIDENTIALITY ORDER IN PLACE

No email, no fu re Negrin IME, various outstanding discovery issues relevant to CSI set aside

treating experts, disclose opinions?

We were going to try and get an MVR and see if we could find out more about why he was sent to defensive driving.

Buchanan Dx post-concussive syndrome but has trouble excluding the pre-existing ADHD, there isn't much of a baseline to work from. No malingering, initial concussion was serious.

Douglas L. Whitt
404-25-XXXX 
12-21-68

DO WE NEED WRITTEN ASSURANCE FROM CSI?  see also file and Fenrir em re driving history

Discovery ran 8/22, do not extend per SKL

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Schuch] get written stipulation of liability, records to physiatrist, retain, OOS 3MM NEED TO RELEASE EVERYONE, FF, SUPPLEMENT, steve wants to try and get depos. see below; PDM to read Navarro deposition, get it ready for trial, maybe edit it for mediation

\item \textit{<2023-05-30 Tue> } Event: [Schuch] pl depos

\item \textit{<2023-07-06 Thu> } Event: [Schuch] mediation

[ ] Gorecki - has not responded, BW is following up
[ ] Cooper - neurologist
[ ] Buchanan - SKL is setting up
[ ] physiatriest - reviewing, BW is following up to set up appointment
[ ] Miranda Reed - maternity leave
[ ] leave urology alone
[ ] supervisor?
[ ] McCord looking at it

Crabtree likes the meds re ortho, urologic issue is probably a non-issue, legit partial disability, does not recall much TBI in the record

Ashley did timeline and found prior accident, contact golf friends and ID them, schedule officer and witness for preservation, doctors. Send PJI and OOS for 1.5MM (wait on mediation)?
\end{itemize}

\subsection*{Smeltzer}
\label{sec:org8579fe3}

\emph{Joseph Smeltzer v. Regina Little and Dream Power Therapy, Inc.}

Client say PT isn't working, they don't want to do injections, and he doesn't want to be "cut on."  ORR if we go forward re liability, but looks like it's just going to be a damages case. ORR sent to Ag, they responded no records bc pending investigation.

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Smeltzer] meet with client re withdraw, dismiss counterclaim? just punt?

\item \textit{<2023-10-18 Wed> } Deadline: [Smeltzer] discovery dl per answer
\end{itemize}

"people don't quit meth"

20 PT, at least one SI joint injxn

SI joint issue is related

\subsection*{Smith, Leah v. NEGMC et al.}
\label{sec:orga3820d3}

\emph{Leah Nicole Smith and Robert Smith, individually and as Wrongful death Claimants in relation to Luke Smith, a Deceased Minor, v. Northeast Georgia Medical Center, Inc., Longstreet Clinic, PC, Zachariah B. Dillard, MD, Whitney L. Dockery, CNM, Sally A. Monroe, CNM, and Mandy R. Whitfield, RN}

\begin{itemize}
\item Attorney for Longstreet, Dillard, Monroe, and Dockery: \href{https://gabar.reliaguide.com/lawyer/30309-GA-Daniel-Huff-283902}{Daniel J. Huff, Huff Powell Bailey LLC}

\item Attorney for Longstreet, Dillard, Monroe, and Dockery: \href{https://gabar.reliaguide.com/lawyer/30309-GA-John-Loftin-250170}{J. Harrison Loftin, Huff Powell Bailey LLC}

\item Attorney for NEGMC and Whitfield: \href{https://gabar.reliaguide.com/lawyer/30309-GA-Michael-Bailey-248155}{M. Scott Bailey, Huff Powell Bailey LLC}

\item Attorney for NEGMC and Whitfield: \href{https://gabar.reliaguide.com/lawyer/30309-GA-Lindsey-Costakos-279062}{Lindsey Cassimus, Huff Powell Bailey LLC}

\item Attorney for NEGMC and Whitfield: \href{https://gabar.reliaguide.com/lawyer/30309-GA-Ethan-Harris-250213}{Ethan D. Harris, Huff Powell Bailey LLC}
\end{itemize}

Smith - ask for policies and practices relating to the use of midwives specific to cost analysis in the past ten years. Send to Practice and hospital

All Ds Answer 2023-03-10: Affidavit defense, claims emergency so clear and convincing / gross negligence. Admit scope as to Whitfield

\begin{itemize}
\item \textit{<2023-05-05 Fri> } Follow up: [Smith] scheduling depos, getting policies supplement (protective order) OOS?

--> discovery re staffing? --> next step, no 6.4 yet per SKL BUT WHEN WE DO BE SURE WE GOT MESSAGES

\item \textit{<2023-11-15 Wed> } Deadline: [Smith] discovery dl per scheduling order --> pl experts by 11/20 --> addl dls to follow
\end{itemize}

\subsection*{Sullen, Mordena v. Adams}
\label{sec:org56cd840}

\emph{Mordena Sullen v. Carla Wilson Adams}

[-] Charges, in limine

[-] Bolden outline

[ ] stip entire record, exhibits from video deposition

[-] video

[ ] specials only 250,000 lost income in PTO, need voir dire re chiro, ask open ended, car travel to visit daughters

Ellis cell 4042734017

\begin{itemize}
\item \textit{<2023-05-03 Wed> } Todo: [Sullen] pp trial \textit{<2023-05-22 Mon> } can we introduce Crabtree as a doctor, supplement chiro, get Fowler live?

\item \textit{<2023-05-16 Tue> } 9:30a Event: [Sullen] meet with clients at Sullen's place re trial prep

talk to girls about human relationship affected by wreck

PROVE THE POLICY - some improvement
\end{itemize}

\subsection*{Wedde v. Sheets}
\label{sec:orgf31a4e6}

Counsel for Ds: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=NDMwOTIz}{Marcia S. Freeman, Waldon Adelman Castilla Hiestand \& Prout}

Counsel for Ds: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=MjM4ODQz}{Ashley L. Yagla, Waldon Adelman Castilla Hiestand \& Prout}

Counsel for UM: \href{https://gabar.org/MemberSearchDetail.cfm?ID=MTQyNTUz}{Jennifer Ann Mills, Law Office of J. Andrew Williams (Nationwide General Insurance Company)} By substitution for Wetzel

DOI 2022-03-26, single car accident wrongful death, waiting on estate in TN (ONE YR STATUTE) and more info re dram shop piece - UM svc filed 10-13

EW dead at scene, no attempt to rescuscitate per no pulse and severe trauma, noted "Obvious Death." Autopsy notes cause of death as blunt force head trauma. Per autopsy

Nationwide says coverage (100k UM) is 0.0 per TN reduced by; State Farm tendered 500k.
\textasciitilde{}
K is 35\% not 40!

Is UM reduced by? LI is 500,000 but it looks like there is another 250k policy in the household

Insurance policy produced and sent to Weston
 \url{https://www.epilepsy.com/lifestyle/driving-and-transportation/laws/georgia} [1]

Nathan Sheets had seizures which were not reported to the dmv prior to the accident
His parents knew of them and still entrusted the vehicle to him.
Nathan in hospital said his accident was caused by a seizure

Per the Order for Mediation of December 20, 2022, counsel for Plaintiff reports that the parties attempted mediation in the above matter on March 29, 2023 and were not successful.

=
--> Follow up: [Wedde] fu re narrowing, scheduling depos? Per Yagla she will not object to us getting parent \#s at depo and will provide prior. review scheduling order, see notes file \href{file:///Users/pmenair/Documents/WORK SYNC/projects/5-CaseFiles/Wedde.org}{TODO}

\begin{itemize}
\item \textit{<2023-05-04 Thu> } Follow up: [Wedde] attend arraignment --> other discovery? waiting on parents for depos, call stephanie, did we send nonparty
\end{itemize}

blood on p. 27, 1.14 value, at 10:00 he was .193-.2, hospital records show intoxicated, should be noticeably intoxicated

\begin{itemize}
\item \textit{<2023-05-17 Wed> } Deadline: [Wedde] 30 days from objection

\item \textit{<2023-06-14 Wed> } Event: [Wedde] Rule Nisi

\item \textit{<2023-06-09 Fri> } Deadline: [Wedde] discovery dl

Copies of Dr. Ramone Sanchez’s (neurologist) medical records. Send a
\end{itemize}
HIPAA release to opposing counsel for Sheets to sign so we can get
these records.

Steve wants copies of Sheets’ prior records of the neurologist who
treated him for seizure condition. Send a supplemental interrogatory
asking who the neurologist was that treated Sheets for his seizures.

Sheets has disciplinary records at the University of TN, Chattanooga
location. Sheets was suspended for the DUI.

There is \$1,250,000 of insurance coverage through Central Mutual Insurance.

Get copies of records from court in TN of prior DUI and plea. Sheets
was suspended from driving for a year.

Sheets also had two prior accidents. Send a supplemental interrogatory
asking who insured him at the time of those first two accidents.

Want all policies of insurance last five years
Like to know who was their agent
Want any and all umbrella policies for last five years.

[ ] employer sending
[ ] school records?
[ ] neuro sending

\subsection*{White v. Caput}
\label{sec:org05da139}

\emph{Neal White, individually and as Natural Guardian of Connor White, a minor v. Nicklas Chaput and Roofing Resources of Georgia}

Counsel for RRG: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=MDIwNzY1}{Adam L. Appel, Dermer Appel Ruder, LLC}

Counsel for Chaput: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=MDYzMTQz}{Jonathan L. Bledsoe, The Minor Firm}

Counsel for Chaput: \href{https://www.gabar.org/MemberSearchDetail.cfm?ID=NjQ5Mjky}{Azurae K. Orie, The Minor Firm}

Chaput answer filed 3/31 with no concerning defenses, last clear chance
RRG answer filed 4-03 with scope of employment defense

RRG discovery - Robin Rich and Carey Rich? Chaput took photos, gave statement to carrier they won't produce, denies scope of employment but admit he was on the way to the office. Refuse to identify a safety director on relevance grounds. No drug/alcohol. Won't identify industry orgs. Won't identify procedure manuals. Won't produce work activity records, claim file, withholds portion of personnel file, all DOT stuff like safety files, etc.

Chaput discovery - he was turning with obstructed vision, client stopped in an unusual place. rogs are fine but he refuses to produce work activity records, etc

\begin{itemize}
\item \textit{<2023-05-03 Wed> } Todo: [White] abusive litigation letter, 6.4, cw skl re OOS and liability defense --> 6.4 or schedule depos --> CALENDAR DL IN SCHEDULING ORDER
\end{itemize}

Get tape

NB HE WAS SUPPOSED TO CARRY 100K, NOT 25K

\begin{itemize}
\item \textit{<2024-05-24 Fri> } Deadline: [White] respond to abusive litigation letter

\item \textit{<2023-10-03 Tue> } Deadline: [White] discovery dl per answers
\end{itemize}

\section*{Prelit}
\label{sec:orgad7a9ed}

\begin{itemize}
\item \textit{<2023-05-03 Wed> } Todo: [Byers] pp compl [waiting on Satterfield, rss re construction permit] - Satterfield picture, too high for handicap, can't exceed 3/4, SHALL have a landing per international building code 10-10.1.6 "Landings and Doors" failure to maintain is in several codes etc ADA even if not open to the public
\end{itemize}

Si  Whelchel Family Trust

no payment for event, no agreement, etc
month to month lease

Loose threshold
they are claiming comp, no comp insurance
w2 and w9 to show employee? volunteer v. employee

waiver
sister lives in Gainesville, was supervisor

Dr. Theopolis and Empting

RSD - Calvare

offer of settlement and PJI 999,999

beneficiary dec action coverage

\url{https://www.swanlakeoverlook.com/}

other employees, etc

Huber v. Phillips et al.

prelit wrongful death CPAP, Multi-District since Oct 2021, need to move on getting an estate and getting medical review \{NOT - get details from client and file without an estate, remember consortium, talk to client first re medical details, device ID); client is \textbf{Angelia} Huber, death date July 27, 2021.

\begin{itemize}
\item\relax [Huber] send to India NO, co-counsel
\end{itemize}
\end{document}